---
title: "Analysis of the World happiness"
author: 'Group 21'
date: "2021/6/24"
output:
  pdf_document: default
  html_document: default
bibliography: reference.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE, comment = NA)
```

```{r libraries}
library(ggplot2)
library(dplyr)
library(moderndive)
library(ISLR)
library(skimr)
library(plotly)
library(tidyr)
library(jtools)
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(corrplot)
library(car)
library(reshape2)
library(knitr)
library(fmsb)
library(maps)
library(mapproj)
library(bibtex)
```

```{r data, echo = FALSE, eval = TRUE}
happiness <- read_csv("Group_21.csv")
```

# Introduction{#sec:Intro}
Happiness depends on many factors in our lives and the things going on in our surrounding world. This world happiness survey gives insights into how happiness changes in our lives. As we know, covid-19 has a huge impact on our lives that it has made us think about people’s subjective well-being in the world and the factors affecting it. More seriously, “As the pandemic struck, there was a large and immediate decline in mental health in many countries worldwide” [@hlsn21]. Therefore, it seems necessary to give more importance to happiness and well-being, thereby better achieving and measuring social and economic development [@gra21]. Our study mainly serves two purposes. One purpose is to find and evaluate the influential factors of happiness. The other is to trace the size and distribution of happiness impacts. We adopt the multiple regression analysis based on the data from the Gallup World Poll. There are six variables to measure happiness scores of 149 countries or territories. After processing the data, we finally get three influential factors.

At first, we choose seven variables with one outcome variable, Happy score and six explanatory variables, they are Logged GDP per capita, Social support, Healthy life expectancy, Freedom to make life choices, Generosity and Perceptions of corruption. The following is interpretations of each variable.

Happy score (score): respondents were asked to rate their possible lives from one to ten, with 1 being the worst and 10 being the best.

Logged GDP per capita (LoggedGDP): it means logged GDP index from 149 countries.

Social support (Social): it means if the participants could find someone’s help when they are in trouble.

Healthy life expectancy (expectancy): it means the expected life expectancy.

Freedom to make life choices (Freedom): it means if the participants are satisfied with their freedom to choose what they do in life.

Generosity: it means if the participants are generous after asking if they have donated money to charity organizations.

Perceptions of corruption (corruption): it means if the participants are conscious of the corruption within the government and business.

# Exploratory Data Analysis {#sec:EDA}
We visualize the values as boxplots:
```{r rename, echo = FALSE, eval = TRUE}
happiness_rename <- happiness %>%
  rename(
    Country_name = 'Country name',
    Regional_indicator = 'Regional indicator',
    Happy_score = score,
    Logged_GDP = LoggedGDP,
    Social_support = Social,
    Healthy_life_expectancy = expectancy,
    Perceptions_of_corruption = corruption
  )
```

```{r boxplot, echo = FALSE, eval = TRUE, out.width = '70%', fig.pos = 'H', fig.align = "center", fig.cap = "\\label{fig:box} Boxplots of six variables."}
data1 <- happiness_rename %>%
  melt(id = c("Country_name", "Regional_indicator", "Happy_score")) %>%
  filter(variable != "Healthy_life_expectancy" & variable != "Logged_GDP")
p1 <- ggplot(data1, aes(x=variable, y=value, fill=variable)) + geom_boxplot(varwidth = TRUE) + guides(fill=F)
p1

data2 <- happiness_rename %>%
  melt(id = c("Country_name", "Regional_indicator", "Happy_score")) %>%
  filter(variable == "Healthy_life_expectancy")
p2 <- ggplot(data2, aes(x=variable, y=value, fill=variable)) + geom_boxplot(varwidth = TRUE) + guides(fill=F)
p2

data3 <- happiness_rename %>%
  melt(id = c("Country_name", "Regional_indicator", "Happy_score")) %>%
  filter(variable == "Logged_GDP")
p3 <- ggplot(data3, aes(x=variable, y=value, fill=variable)) + geom_boxplot(varwidth = TRUE) + guides(fill=F)
p3

```
Figure 1 shows the descriptive statistics of four variables like Social support, Freedom, Generosity and Perceptions of corruption. It is obvious that apart from Generosity, people in more than half of the countries grade more than 0.6 on Social support, Freedom and Perceptions of corruption although there are some outliers lower than 0.5. And figure 2 shows half of the population has a life span of 60 to 70 years. The figure 3 shows the median of Logged GDP is near 9.5.

Next we use table to illustrate the details of all seven variables.
```{r, echo = FALSE, eval = TRUE,warning = FALSE, message = FALSE}
summary(happiness[3:9]) %>%
kable(caption = '\\label{tab:summaries} Summary statistics for observations with chosen variables.') %>%
  kable_styling(latex_options = "hold_position", full_width = F, font_size = 8)

```
Table 1 describes some basic features of those variables. For example, the average happiness score is 5.533 and the median is 5.534. It demonstrates that people’s feelings of happiness or subjective well-beings are neither high nor low.

# Visualization of the data {#sec:VIS}
We can visualize our data by producing histogram and radarplot, where seeing as we have several countries, we shall plot the bars or lines using different colours for each country: 
```{r barplot, echo = FALSE, eval = TRUE, out.width = '70%', fig.pos = 'H', fig.align = "center", fig.cap = "\\label{fig:bar} The 5 happiest contries."}
ggplot(head(happiness_rename,5), aes(x = Country_name, y =Happy_score))+
  geom_bar(stat="identity", aes(reorder(Country_name, - Happy_score), fill = Country_name))+
  geom_text(aes(label = Happy_score), vjust=-0.2, size = 5 )+
  theme(axis.title =element_text(size=14), axis.text=element_text(size=14))+
  guides(fill=F)
```
Figure 4 shows the top 5 happiest countries. Finland gets the highest happy score with 7.842, followed by Denmark at 7.62. in addition, the differences between those five countries are small, less than 0.4, and all scores are greater than 7.4. 
```{r barplot2, echo = FALSE, eval = TRUE, out.width = '70%', fig.pos = 'H', fig.align = "center", fig.cap = "\\label{fig:bar} The 5 most unhappy contries."}
ggplot(tail(happiness_rename,5), aes(x = Country_name, y =Happy_score))+
  geom_bar(stat="identity", aes(reorder(Country_name, - Happy_score), fill = Country_name))+
  geom_text(aes(label = Happy_score), vjust=-0.2, size = 5)+
  theme(axis.title =element_text(size=14), axis.text=element_text(size=14))+
  guides(fill=F)
```
Figure 5 shows the five most unhappy countries. Afghanistan takes the position as the most unhappy country with the score of 2.523. And the other four countries have similar scores lower than 3.6. Other than Afghanistan from South Asia, other four countries are in Africa.
```{r radarplot, echo = FALSE, eval = TRUE, out.width='80%',fig.pos = 'H', fig.align = "center", fig.cap = "\\label{fig:radar} Comparisons between Finland and the UK from six indexes."}
data4 <- happiness_rename[, 4:9]
maxm <- apply(happiness_rename[,4:9], 2, max)
minm <- apply(happiness_rename[,4:9], 2, min)
data5 <- rbind(maxm, minm, data4[1,], data4[17,])

colors_border = c('#f19cbb', '#0099ff')
colors_in = c('#f19cbb55', '#0099ff1a')
radarchart( data5, axistype=6, pcol= colors_border, 
            pfcol= colors_in, plwd=2, plty=1, cglcol="grey", 
            cglty=1, axislabcol="grey", vlcex=0.8 
)

legend(x=1.5, y=1.1, legend = c("Finland", "UK"), bty = "n", 
       pch=20, col=colors_in , text.col = "black", cex=0.8, pt.cex=3)

```
Figure 6 compares those six dimensions that Finland obtains with those that UK obtains. There are obvious differences between the perceptions of corruption and generosity, with the UK getting relatively much higher values. Conversely, when referring to Freedom indicators, Finland has a slightly higher value. Besides, it owns similar grades among the other three aspects.

```{r map, echo = FALSE, eval = TRUE, out.width='70%',fig.pos = 'H', fig.align = "center", fig.cap = "\\label{fig:map} World happiness score map."}
WorldData <- map_data('world')
happiness<-read.csv("Group_21.csv")
df<-select(happiness, region=Country.name,value=score)

Total <- WorldData[WorldData$region %in% df$region, ]
Total$value <- df$value[match(Total$region, df$region)]

  ggplot() +
  geom_map(data = WorldData, map = WorldData,
           aes(x = long, y = lat, group = group, map_id=region),
           fill = "white", colour = "black", size=0.5) + 
  geom_map(data = df, map=WorldData,
           aes(fill=value, map_id=region),
           colour="black", size=0.5) +
  coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90)) +
  scale_fill_continuous(low="darkred", high="thistle1", guide="colorbar") +
  scale_y_continuous(breaks=c()) +
  scale_x_continuous(breaks=c()) +
  labs(fill="Score", title="World Happiness Report 2021", x="", y="") +
  theme_dark()
```
Figure 7 has displayed a happiness score map globally based on the World Happiness Report 2021. We can see that most countries in the western area have high scores whereas the eastern countries have low scores, which demonstrates that people in western countries lead happier and more fulfilling lives.

# Formal Data Analysis {#sec:FDA}
To begin to analysis the world happiness dataset, we need to check the correlation between the six explanatory variables to avoid the problem of multicollinearity.
```{r corrplot, echo = FALSE,eval = TRUE, out.width = '70%', fig.pos = 'H', fig.align = "center", fig.cap = "\\label{fig:corr} Correlation coefficient table."}
happiness[,4:9]%>%
  cor()%>%
  corrplot(method = "number")
```
From our correlation table we can see that the correlation between our Logged GDP and Healthy life expectancy is 0.859, which is a strong positive linear relationship. And the Logged GDP and Social support also have the high degree of collinearity. The correlation between this two variables is 0.785. So we remove Healthy life expectancy and Logged GDP. Then, using the remaining 4 explanatory variables to perform stepwise regression, and observe whether the remaining variables need to be eliminated.
```{r,echo=FALSE}
model<-lm(score~Social+Freedom+Generosity+corruption,data=happiness)
step(model)
```
According to the results of stepwise regression, we choose the model with the smallest AIC as the final model.Then,we fit the following linear model to the data.
$$\widehat{\mbox{score}}_{\mbox{i}} = \widehat{\alpha} +
{\widehat\beta}*{\mbox{Social}}_{\mbox{i}} +\widehat{\gamma}*{\mbox{Freedom}}_{\mbox{i}}+\widehat{\delta}*{\mbox{corruption}}_{\mbox{i}}$$

where

• the $\widehat{\mbox{score}}_{\mbox{i}}$: the happiness score of the $i\mbox{th}$ country.

• the $\widehat{\alpha}$: the intercept of the regression line.

• the $\widehat{\beta}$: the coefficient for the first explanatory variable ${\mbox{Social}}$.

• the $\widehat{\gamma}$: the coefficient for the second explanatory variable ${\mbox{Freedom}}$.

• the $\widehat{\delta}$: the coefficient for the second explanatory variable ${\mbox{corruption}}$.

When this model is fitted to the data, the following estimates of ${\alpha}$  (intercept) and ${\beta}$,${\gamma}$ and ${\delta}$ are returned:

```{r,echo=FALSE,fig.width = 13, fig.align = "center",fig.cap = "\\label{fig:resids} Scatterplots of the residuals by Position (left) and a histogram of the residuals (right)."}
model<-lm(score~Social+Freedom+corruption,data=happiness)
get_regression_table(model)%>%
  kable(caption = '\\label{tab:reg} Estimates of the parameters from the fitted linear
regression model.') %>% kable_styling(latex_options = 'HOLD_position')
```
According to this table, the coefficient for social support tells us that, taking all other variables in the model into account and holding them constant, there is an associated increase. On average, every increase of 1 unit in the social support score increases the happiness index score by approximately 5.63 units. In the same way, when the freedom score of life choice increases by 1 unit, the happiness index score also increases by approximately 2.23 units. On the contrary, for every increase of 1 unit in the score for corruption, the total score of happiness index decreases by 1.23 units.

Before we can continue to use the fitted model, we must check the model's assumptions. It is best to consider these according to the residual plot in Figure 9.
```{r residplots,echo=FALSE, fig.width = 13, fig.align = "center",fig.cap = "\\label{fig:resids} Scatterplots of the residuals by Social,Freedom,corruption,fitted value and the histogram of residuals.", fig.pos = 'H', message = FALSE}
regression.points <- get_regression_points(model)
p1 <- ggplot(regression.points, aes(x = Social, y = residual)) +
      geom_jitter(width = 0.5) +
      labs(x = "Social", y = "Residual") +
      geom_hline(yintercept = 0, col = "blue")
p2 <- ggplot(regression.points, aes(x = Freedom, y = residual)) +
      geom_jitter(width = 0.5) +
      labs(x = "Freedom", y = "Residual") +
      geom_hline(yintercept = 0, col = "blue")
p3 <- ggplot(regression.points, aes(x = corruption, y = residual)) +
      geom_jitter(width = 0.5) +
      labs(x = "corruption", y = "Residual") +
      geom_hline(yintercept = 0, col = "blue")
p4<-ggplot(regression.points, aes(x = score_hat, y = residual)) +
  geom_point() +
  labs(x = "Fitted values", y = "Residual") +
  geom_hline(yintercept = 0, col = "blue", size = 1) 
p5<-ggplot(regression.points, aes(x = residual)) +
      geom_histogram(color = "white") +
      labs(x = "Residual")
grid.arrange(p1,p2,p3,p4,p5,ncol = 2)
```
The assumptions of the residuals having mean zero and constant variability across all values of the explanatory variable appear to be valid in this case. According to the three different explanatory variables scatter plots, it can be concluded that the residuals are uniformly distributed above and below the zero line, so the mean is 0. The residuals are randomly distributed around the zero line, and the distribution of the residuals is constant across all fitted values, so there is no obvious pattern or change in the variant. And also the histogram supports the assumption of normal distribution error.

After hypothesis testing, we will analyze the confidence interval and set the confidence level to 95%.
```{r ci, echo=FALSE}
confint(model,level = .95)
```
The data in the table shows that the coefficient range of Social support affecting happiness score is 4.64 to 6.61, and the coefficient range of Freedom is 1.16 to 3.29. The most explanatory variable corruption affects the corresponding variable in the range of -1.83 to -0.62. The interval does not contain 0, indicating that the selected independent variables and their coefficients are valid, and as analyzed above, their given coefficients are the mean value of the interval.

# Conclusions {#sec:Conc}
In our study, to explore what will influence people’s evaluations of happiness, we have used six indicators to measure the happiness score. We have used the stepwise regression analysis to select variables. Then, we fit the multiple linear models with three factors as Social, Freedom, and corruption. It can be concluded that social support and freedom to make life choices are positively related to people’s happiness and perceptions of corruption which can affect the happiness score. In other words, if a person could get help whenever required or if a person is free to make their own choices, they will perceive contented and joyful life. If we consider interpersonal relationships and emotional needs, the results appear to be reasonable and significant. Besides, if a person believes that their government or companies are corrupt, there will be a decline in the happiness score. Personal level provides better insights on the above all results. According to country-level statistics, residents of western countries lead a happier life than eastern, especially those from Northern European nations like Finland and Denmark. Furthermore, the size of happiness obtained by the top five countries is three times larger than that obtained by the bottom five nations. It shows there is such a huge gap in individual happiness and satisfaction globally.

# Extend of study {#sec:ES}
In the future we can consider more factors to have better insights on this happiness report such as the population of the country: as population increases the diversity increases and getting the same facilities for everyone becomes difficult because of less number of resources and more number of people, facilities available in a country: as European countries can have better facilities because they can plan their facilities as the population is very less, the effect of natural calamities: some countries will face extreme conditions such as flood, tsunami, etc. frequently which affects human life, the effect of pollution: Population affects the environment and eventually affects human life.

We can use a different approach and also can fit different models by considering the topics mentioned above.Moreover, our study could be improved by adding the individual’s daily happiness score, not just the average happiness scores based on countries. Besides, it will be useful to consider the death rate among every nation so that we could better understand the influence of covid-19 pandemic has on happiness score index.

# Reference {#sec:RE}
\bibliography{reference}
